---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
suppressPackageStartupMessages(library(tidyverse))

csv_file <-"https://docs.google.com/spreadsheets/d/e/2PACX-1vQIZsfs03hwVb60mhPCZ_w4Fm_g9P0vCykAxJ-h9xJyj_RufEF8dXmcLybF2404j7Z2qoGwAVQL8Tpf/pub?output=csv"

latest_data <- read_csv(csv_file, show_col_types = FALSE) %>%
    rename(
    timestamp = 1,
    industry = 2,
    word_count = 3,
    has_emoji = 4
  )




```{css}


body {
  font-family: 'Arial', sans-serif;
  color: #333333;
  text-align: center;
}
h2 {
  color: #2c3e50;
  border-bottom: 2px solid #3498db;
  padding-bottom: 5px;
}


```

## Tracking Promotional Email Trends

This report tracks promotional emails over time, looking at which industries send the most emails and how often they use emojis in the subject line.


```{r}
# Calculate summary values using Lab 2A and 2B functions
total_emails <- nrow(latest_data)
avg_word_count <- (sum(latest_data$word_count) / length(latest_data$word_count)) %>% round(1)

max_words <- max(latest_data$word_count)
min_words <- min(latest_data$word_count)
total_responses <- length(latest_data$industry)




paste("Based on the data collected, I have tracked a total of", total_emails, "promotional emails in 5. The average subject line length across all industries is", avg_word_count, "words.")

paste("Based on the data collected, I tracked a total of",
                          total_emails,
                          "promotional emails with an average length of",
                          avg_word_count,
                          "words.",
                          "The longest subject line I received contained", 
                          max_words, 
                          "words, while the shortest contained only", 
                          min_words, 
                          "words.")



# Chart 1: Horizontal bar chart 
ggplot(data = latest_data) +
  geom_bar(aes(y = industry, fill = industry)) +
  labs(
    title = "Promotional Emails by Industry",
    x = "Number of Emails",
    y = "Industry Type"
  )

# Chart 2: Vertical bar chart 
ggplot(data = latest_data) +
  geom_bar(aes(x = has_emoji, fill = has_emoji)) +
  labs(
    title = "Emoji Usage in Subject Lines",
    x = "Contains Emojis?",
    y = "Number of Emails"
  )

```



