---
title: My dynamic report
output: html_fragment
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```







```{css}
body {
  font-family: 'Arial', sans-serif;
  color: #333333;
  text-align: center;
}
h2 {
  color: #2c3e50;
  border-bottom: 2px solid #3498db;
  padding-bottom: 5px;
}
```

## Tracking Promotional Email Trends

This report tracks promotional emails over time, looking at which industries send the most emails and how often they use emojis in the subject line.
```{r}
csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQIZsfs03hwVb60mhPCZ_w4Fm_g9P0vCykAxJ-h9xJyj_RufEF8dXmcLybF2404j7Z2qoGwAVQL8Tpf/pub?output=csv"

latest_data <- read_csv(csv_file) %>%
  rename(
    timestamp = 1,
    industry = 2,
    word_count = 3,
    has_emoji = 4
  )


total_emails <- nrow(latest_data)
avg_word_count <- round(sum(latest_data$word_count) / length(latest_data$word_count), 1)
max_words <- max(latest_data$word_count)
min_words <- min(latest_data$word_count)

paste("Based on the data collected, I received a total of",
      total_emails,
      "promotional emails with an average length of",
      avg_word_count,
      "words.",
      "The longest subject line I received contained",
      max_words,
      "words, while the shortest contained only",
      min_words,
      "words.")

ggplot(data = latest_data) +
  geom_bar(aes(y = industry, fill = industry)) +
  labs(
    title = "Promotional Emails by Industry",
    x = "Number of Emails",
    y = "Industry Type"
  )

ggplot(data = latest_data) +
  geom_bar(aes(x = has_emoji, fill = has_emoji)) +
  labs(
    title = "Emoji Usage in Subject Lines",
    x = "Contains Emojis?",
    y = "Number of Emails"
  )
```

## analysis

- Based on the bargraph generated, we can clearly see that the food/delievery category have most promotional emails where it have 12 emails which is rouphly a third of the entire dataset. meanwhile the the software/tech category have 6 emails, the "other" category have 7 emails, "travel" category have 4 emails, Job advertising category have 3 emails and clothing/retail category have the fewest email which only have 2 emails. out of all 34 promotional emails. 


- We can also see that from another bargraph generated, there is a evidence that using emojis in the email will captures the reader's attention. Out of 34 promotional emails 19 included an emoji in the subject line to only 15 that did not put an emoji in the subject line, suggesting that over half the emails are trying to use emojis to catch readers attention 

## conclusion

in conclusion, the two bargraphs shows a clear trend with 34 promotional emails where the first graph shosws that the food industtry are having the most tracing emails suggesting that my email inbox is being targeted mainly by the food and delievery services and there are more emails using emoji to attract reader compare to the ones that don't use emojis we can also conclude marketers are more willing to use emojis to attract reader's attention


